\documentclass[line]{res}
\usepackage{enumerate}
%\usepackage{times}

\usepackage[top=1.25in, bottom=1.25in, left=1in, right=1in]{geometry}
\usepackage{verbatim}
\usepackage{url}
\usepackage{longtable}
\usepackage{lipsum}

%Font
\usepackage[sc]{mathpazo}
\usepackage{courier}

%\oddsidemargin -.5in
%\evensidemargin -.5in
%\bottommargin -0.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0.07in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
		\setlength{\topsep}{0.07in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.0in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0in}}}{\end{list}}

\begin{document}

\renewcommand{\sc}{}
\name{{\Large Chen Lian} \vspace{.08in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
{\it Address:} 
Department of Economics, University of California, Berkeley\\
$~$ \hspace{12mm}
675 Evans Hall, University Dr \\
$~$ \hspace{12mm} 
Berkeley, CA 94720
$~$ \hspace{12mm} \\
  {\it E-mail:} \url{chen_lian@berkeley.edu} \\       
  {\it Website:} \url{https://sites.google.com/view/chenlian/home} \\
  {\it Google scholar:} \url{https://scholar.google.com/citations?user=z3yCoXYAAAAJ&hl=en&oi=sra} 


\section{\sc Academic Positions}

\begin{list1}

\item[] 
\textbf{University of California, Berkeley.} Assistant Professor of Economics (2020--).\\
 Research interests: Macroeconomics, Monetary Economics, Behavioral Economics, Finance.
\vspace{0.2cm}
\item[]
\textbf{National Bureau of Economic Research.} Faculty Research Fellow (2021--). \\
 Programs: Monetary Economics, Economic Fluctuations and Growth.
\end{list1}
\section{\sc Education} 

\begin{list1}
\item[]
\textbf{Massachusetts Institute of Technology}, Cambridge, MA. \\
Ph.D. in Economics, 2020.
\vspace{0.2cm}
\item[]
\textbf{Massachusetts Institute of Technology}, Cambridge, MA.\\
B.S. in Economics, 2015; B.S. in Mathematics, 2015. 
\end{list1}

\section{\sc Working Papers} 
\begin{list1}
\item[] \textbf{Sophiscated Borrowing Constraints and Macroeconomic Dynamics,} with Mahdi Ebsim, Yueran Ma, Pablo Ottonello, and Diego Perez. 
\vspace{0.2cm} 
\item[] \textbf{Fiscal Inaction as Monetary Support,} with George-Marios Angeletos and Christian Wolf.  
\vspace{0.2cm}
\item[] \textbf{Borrowing Constraints, Markups, and Misallocation,} with Huiyu Li, Yueran Ma and Emily Martell.
\vspace{0.2cm}
\item[] \textbf{Deficits and Inflation: HANK meets FTPL,} with George-Marios Angeletos and Christian Wolf.

\end{list1}

\section{Publications}

\begin{list1}

\item[] \textbf{Why do Workers Dislike Inflation? Wage Erosion and Conflict Costs,} with Joao Guerreiro, Jonathon Hazell, and Christina Patterson. Forthcoming at \emph{Econometrica}.
\vspace{0.2cm}
\item[] \textbf{Beliefs about the Economy are Excessively Sensitive to Household-level Shocks: Evidence from Linked Survey and Administrative Data,} with Dmitry Taubinsky, Luigi Butera and Matteo Saccarola. Forthcoming at \emph{Quarterly Journal of Economics}.

\item[] \textbf{The Economics of Financial Stress,} with Dmitriy Sergeyev and Yuriy Gorodnichenko. \emph{Review of Economic Studies}. October 2025.
\vspace{0.2cm}

\item[] \textbf{Can Deficits Finance Themselves?} with George-Marios Angeletos and Christian Wolf. \emph{Econometrica}. September 2024. 
\vspace{0.2cm}

\item[] \textbf{Bankruptcy Resolution and Credit Cycles}, with Martin Kornejew, Yueran Ma, Pablo Ottonello and Diego Perez. \emph{NBER 39th Annual Conference on Macroeconomics}, 2024.
\vspace{0.2cm}

\item[] \textbf{Mistakes in Future Consumption, High MPCs Now.} \emph{American Economic Review: Insights}. December 2023.  
\vspace{0.2cm}

\item[] \textbf{Determinancy without the Taylor Principle,} with George-Marios Angeletos. \emph{Journal of Political Economy}. August 2023.

\vspace{0.2cm}

\item[] \textbf{Dampening General Equilibrium: Incomplete Information and Bounded Rationality,} with George-Marios Angeletos. \emph{Handbook of Economic Expectations}. January 2023.

\vspace{0.2cm}

\item[] \textbf{Confidence and the Propagation of Demand Shocks,} with George-Marios Angeletos. \emph{Review of Economic Studies}. May 2022.
\vspace{0.2cm}

\item[] \textbf{A Theory of Narrow Thinking.}  \emph{Review of Economic Studies}. October 2021 (Feature Article).
\vspace{0.2cm}


\item[] \textbf{Anatomy of Corporate Borrowing Constraints,} with Yueran Ma. \emph{Quarterly Journal of Economics,} February 2021.
\vspace{0.2cm}
\item[] \textbf{Low Interest Rates and Risk Taking: Evidence from Individual Investment Decisions,} with Yueran Ma and Carmen Wang. \emph{Review of Financial Studies}, June 2019 (Lead article).
\vspace{0.2cm}

\item[] \textbf{Forward Guidance without Common Knowledge,} with George-Marios Angeletos. \emph{American Economic Review}, September 2018.
\vspace{0.2cm}

\item[]
\textbf{Incomplete Information in Macroeconomics: Accommodating Frictions in Coordination,} with George-Marios Angeletos. \emph{Handbook of Macroeconomics, Volume 2}, October 2016.

\end{list1}

\section{Work in Progress}

\begin{list1}

\item[] \textbf{Forecasting Inflation with Microdata: An Adaptive Machine Learning Approach,} with Catherine Chen, Chen Gao, Jonathon Hazell, and Lihua Lei.
\vspace{0.2cm}
\item[] \textbf{Importing Aggregate Demand,} with Dmitry Mukhin and Christian Wolf.
\vspace{0.2cm}
\item[] \textbf{Revisiting Monetary-Fiscal Interactions and Equilibrium (In)Determinacy,} with George-Marios Angeletos, Christian Wolf, and Dalton Zhang.
\vspace{0.2cm}
\item[] \textbf{The Macroeconomic Effect of AI: Sizing the Software Engineering Channel,} with Alex Blumenfeld, Jonathon Hazell, and Andreas Schaab.
\vspace{0.2cm}
\item[] \textbf{Regulating AI: International Competition and Geopolitics,} with Andreas Schaab.


\end{list1}


% \section{\sc Permanent Working Papers} 
% \begin{list1}
% \item[] \textbf{Consumption with Imperfect Perception of Wealth,} December 2019, subsumed into "Mistakes in Future Consumption, High MPCs Now."


% \item[] \textbf{Dampening General Equilibrium,} with George-Marios Angeletos, May 2017, subsumed into "Dampening General Equilibrium: Incomplete Information and Bounded Rationality."
% \end{list1}

\section{\sc Comments and Conference Volumes} 
\begin{list1}
\item[] Comments on \textbf{“Fiscal and Monetary Stabilization Policy at the Zero Lower Bound: Consequences of Limited Foresight”} by Woodford and Xie, \emph{Journal of Monetary Economics: Carnegie-Rochester Conference Series on Public Policy}, 2022.
\end{list1}


\section{\sc Conference and Seminar}

\begin{list1}
\item [2026]
\begin{list2}
\item[] Berkeley-Stanford Macroeconomics Conference, Bravo Center Workshop on Behavioral Economics, CEMFI, Federal Reserve Bank of Atlanta, Federal Reserve Bank of New York, Macroeconomic Relevance of Measured Beliefs Conference, NBER Behavioral Finance Meeting (discussant), NBER Long-Term Fiscal Policy Meeting, NBER Monetary Economics Spring Meeting, Northwestern University, Reykjavik Economic Conference, Santa Clara University, SED, Stanford GSB, UC Berkeley, UC Davis, UC3M, the WashU \& St. Louis Fed Conference on Macroeconomics
\end{list2}

\item[2025]
\begin{list2}
\item[] AEA, Banco de Portugal, Banco de Portugal Monetary Conference (discussant), CREI, Duke University, e61 Institute, Federal Reserve Bank of St. Louis, Federal Reserve Board, Hydra Workshop on Dynamic Macroeconomics (discussant), Methods and Applications for DSGE Models workshop at Federal Reserve Bank of Philadelphia (discussant), Micro 4 Macro Workshop, NBER Behavioral Finance Spring Meeting, NBER Monetary Economics Spring Meeting, NBER Monetary Economics Fall Meeting (discussant), NBER Summer Institute (Behavioral Macroeconomics; Impulse and Propagation Mechanism; Micro Data and Macro Models; Macroeconomics and Productivity), NSD at Peking University, SED, UC Berkeley, UC Santa Cruz, UCSD 
\end{list2}

\item[2024]
\begin{list2}
\item[] AEA, BSE Summer Forum (ADEMU), CEBRA Webinar, Federal Reserve Bank of Boston, Federal Reserve Bank of Chicago, Federal Reserve Bank of Minneapolis, IMF Conference on Fiscal Policy and Sovereign Debt, Imperial College London, LSE, NBER 39th Annual Conference on Macroeconomics, NBER Summer Institute (Impulse and Propagation Mechanism; Monetary Economics), Northwestern University, SED, Stanford Macro-Finance Junior Conference, The 12th Annual CIGS conference on Macroeconomic Theory and Policy, The 12th Rome Conference on Macroeconomics (Pizzanomics), UC Berkeley, UCL, UT Austin, University of Chicago (Workshop in Macro/International Economics; Behavioral Economics Seminar), SITE (Fiscal Sustainability; Psychology and Economics), Yale University, University of Tokyo, University of Wisconsin-Madison
\end{list2}

\item[2023]
\begin{list2}
\item[] AFA (discussant), Behavioral Economics Annual Meeting, Biennial Consumer Finance and Macroeconomics Conference, Bocconi, Boston College, CKGSB, Columbia (Money-Macro Workshop and Cognition and Decision Lab), Dartmouth, Indiana University Bloomington, LAEF 2nd Annual Junior Workshop in Macroeconomics, NBER Ef\&G Fall Meeting; NBER International Finance and Macroeconomics Fall Meeting (discussant); NBER Monetary Economics Spring Meeting, NYU, Psychology and Economics of Poverty Convening, SITE Fiscal Sustainability, Stony Brook Workshop on Learning and Bounded Rationality, UC Berkeley
\end{list2}

\item[2022]
\begin{list2}
\item[] AEA, AFR International Conference of Economics and Finance, Brown, China International Conference in Macroeconomics, Conference in Honor of Marvin Goodfriend at the Federal Reserve Bank of Richmond, IMF, Maryland, Miami Behavioral Finance Conference, NBER Behavioral Finance Fall Meeting, NBER Ef\&G Spring Meeting, NBER Summer Institute (Behavioral Macroeconomics, discussant; Impulse and Propagation Mechanism), Princeton, SED, Stanford, Tsinghua University, UC Berkeley, UC Davis, UCLA, University of Warwick, UT Austin, Wharton
\end{list2}

\item[2021]
\begin{list2}
\item[] Carnegie-Rochester Conference Series on Public Policy (discussant), China International Conference in Macroeconomics, Federal Reserve Bank of San Francisco, Hitotsubashi University, LSE, Miami Behavioral Finance Conference (discussant), Minnesota Workshop in Macroeconomic Theory, NBER Summer Institute (Impulse and Propagation Mechanism), Pontifical Catholic University of Chile, SED, SFS cavalcade (discussant), UC Berkeley, USC, VEAMS
\end{list2}

\item[2020]
\begin{list2}
\item[] Berkeley-Chicago Behavioral Economics, Boston University, Chicago Booth, Columbia, Duke, Duke Fuqua, Florida State, NBER Monetary Economics Fall Meeting, NBER Summer Institute (Impulse and Propagation Mechanism), BI Norwegian Business School- Norges Bank-University of Oslo, China Star Tour, Stanford GSB, UC Berkeley, Yale SOM
\end{list2}

\item[2019] 
\begin{list2}
\item[] AEA, MIT, St. Louis Fed
\end{list2}

\item[2018] 
\begin{list2}
\item[] AEA, BSE Summer Forum, Bank of Canada (discussant), D-TEA, NBER Monetary Economics Spring Meeting, NBER Summer Institute (Impulse and Propagation Mechanism), SED
\end{list2}

\item[2017] 
\begin{list2}
\item[] AEA, Banque de France, Cowles Foundation (Macroeconomics), ECB, NBER Ef\&G Spring Meeting, NBER Monetary Economics Fall Meeting, NBER Summer Institute (Risks of Financial Institutions \& Impulse and Propagation Mechanism), SED
\end{list2}

\item[2016] 
\begin{list2}
\item[] Econometric Society, NBER Behavioral Finance Fall Meeting, NBER Summer Institute (Impulse and Propagation Mechanism), SED
\end{list2}


\end{list1}

\section{\sc Conference Organization}
\begin{list1}
\item[2026]  
\begin{list2}
\item[] SED Program Committee
\end{list2}
\item[2025]  
\begin{list2}
\item[] SED Session at ASSA
\end{list2}
\item[2024]  
\begin{list2}
\item[] NBER Monetary Economics Fall Meeting
\end{list2}
\end{list1}


\section{\sc Teaching}
\begin{list1}
\item[2026]  
\begin{list2}
\item[] Econ 236B, Advanced Macroeconomics II
\vspace{0.2cm}
\item[] Econ 138, Financial and Behavioral Economics
\vspace{0.2cm}
\item[] NBER Behavioral Macroeconomics Research Boot Camp
\end{list2}

\item[2025]  
\begin{list2}
\item[] Econ 236B, Advanced Macroeconomics II
\vspace{0.2cm}
\item[] Econ 138, Financial and Behavioral Economics
\end{list2}

\item[2024]  
\begin{list2}
\item[] NBER Behavioral Macroeconomics Research Boot Camp
\end{list2}

\item[2023]  
\begin{list2}
\item[] Econ 236B, Advanced Macroeconomics II
\vspace{0.2cm}
\item[] Econ 138, Financial and Behavioral Economics
\end{list2}

\item[2022]  
\begin{list2}
\item[] Econ 138, Financial and Behavioral Economics
\vspace{0.2cm}
\item[] NBER Behavioral Macroeconomics Research Boot Camp
\end{list2}

\item[2021]  
\begin{list2}
\item[] Econ 236D, Behavioral Macroeconomics
\end{list2}

\end{list1}

\section{\sc Ph.D. Advising}
\begin{list1}
\item[2026] Emily Martell (Carleton University)

\item[2023] Jianlin Wang (Santa Clara University)

\item[2022] Seung Joo Lee (Oxford Said)

\end{list1}
\section{\sc Editorial Services}
\begin{list1}
\item[2025-2026] Associate Editor, Journal of the European Economic Association
\end{list1}
\section{\sc Referee Services}
\begin{list1}
\item[] American Economic Review, Econometrica, Quarterly Journal of Economics, Journal of Political Economy, Review of Economic Studies, American Economic Review: Insights, Journal of Finance, Journal of Financial Economics, Review of Financial Studies, American Economic Journal: Macroeconomics, American Economic Journal: Applied Economics, Journal of Economic Theory, Journal of Monetary Economics, Review of Economics and Statistics, Journal of International Economics, Journal of Mathematical Economics, Theoretical Economics, Journal of Economic Dynamics and Control, Economic Journal, Quantitative Economics.

\end{list1}


\section{\sc Grant reviewer}
\begin{list1}
\item[] National Science Foundation, Alfred P. Sloan Foundation, Israel Science Foundation

\end{list1}

\section{\sc Academic Visits}


\begin{list1}
\item[2025] Federal Reserve Bank of San Francisco (Visiting Scholar)

\item[2023-2024] Northwestern (full-year)

\item[2024] Federal Reserve Bank of Minneapolis (1-week), Uchicago BFI Institute (2-week), Yale Cowles Foundation (1-week)

\item[2023] Columbia (3-week), NYU (1-week)

\item[2022] IMF (1-week), Uchicago BFI Institute (1-week), Yale SOM (1-week)

\end{list1}

\section{\sc Awards, Fellowship, and Grants}

\begin{list1}
   \item[2026]
   \begin{list2}
   \item[] Excellence in Refereeing Award, \emph{American Economic Review}
   \end{list2}
\end{list1}

\begin{list1}
   \item[2025] Sloan Research Fellowship
   %(\$75,000)
   \begin{list2}
   \vspace{0.2cm}
   \item[] The SCOR-PSE Junior Research Prize, "Why do Workers Dislike Inflation? Wage Erosion and Conflict Costs," with Joao Guerreiro, Jonathon Hazell and Christina Patterson
   \vspace{0.2cm}
   \item[] Society of Hellman Fellows
   % \item[] UC Berkeley Monetary Economics Grant (\$25,000)
   % \vspace{0.2cm}
   \end{list2}
\end{list1}

\begin{list1}
   \item[2024] 
   \begin{list2}
   \item[] NBER-OFR Market Frictions and Financial Risk Grant, "The Macroeconomic Implications of Corporate Debt Contracts," with Yueran Ma, Pablo Ottonello and Diego Perez 
   % \item[] Clausen Center Grant (\$10,000)
    \end{list2}
\end{list1}

% \begin{list1}
%    \item[2023] 
%    \begin{list2}
%    \item[] UC Berkeley Monetary Economics Grant (\$10,000)
%    \vspace{0.2cm}
%    \item[] Clausen Center Grant (\$5,000)
%    \end{list2}

% \end{list1}

\begin{list1}

\item[2022]

\begin{list2}
\item[] Excellence in Refereeing Award, \emph{American Economic Review}
\vspace{0.2cm}
\item[] Excellence in Refereeing Award, \emph{Review of Economic Studies}
\vspace{0.2cm}
\item[] CICM 2022 Best Paper Award

\end{list2}

\item[2021] Alfred P. Sloan Foundation: "Behavioral Macroeconomics: Methodology and Policy Implications"
%(\$248,662)
\begin{list2}
 \vspace{0.2cm}
\item[] Sapere Aude, DFF-Starting Grant: "The Beliefs Lab: Measuring the Evolution and Impact of Beliefs on the Economy," with Luigi Butera, Birthe Larsen, and Dmitry Taubinsky 
%(\$952,894)
% \vspace{0.2cm}
% \item[] Clausen Center Grant 
%(\$10,000)
\vspace{0.2cm}
\item[] CICM 2021 Best Junior Scholar Paper Award
\end{list2}

\item[2020]
\begin{list2}
\item[] Robert M. Solow Prize for Excellence in Graduate Research and Teaching
\vspace{0.2cm}

\item[] China Star Tour

\end{list2}
\item[2019] 
\begin{list2}
\item[] Alfred P. Sloan Foundation Pre-doctoral Fellowship in Behavioral Macroeconomics
\end{list2}

\item[2017] 
\begin{list2}
\item[] WFA Cubist Systematic Strategies PhD Candidate Award for
Outstanding Research
% \vspace{0.2cm}
% \item[] George and Obie Shultz Fund
\end{list2}

% \item[2016] 
% \begin{list2}
% \item[]  Gregory K. Palm Fellow
% \vspace{0.2cm}

% \item[] George and Obie Shultz Fund
% \end{list2}

% \item[2015] 
% \begin{list2}
% \item[]  MIT Presidential Fellow
% \vspace{0.2cm}
% \item[] George and Obie Shultz Fund
% \vspace{0.2cm}
% \item[]  Phi Beta Kappa
% \end{list2}



\end{list1}

\section{\sc Date}

\begin{list1}
\item[] 06/03/2026
\end{list1}

\end{resume}

\end{document}
