\documentclass[line]{res}
\usepackage{enumerate}
%\usepackage{times}

\usepackage[top=1.25in, bottom=1.25in, left=1in, right=1in]{geometry}
\usepackage{verbatim}
\usepackage{url}
\usepackage{longtable}
\usepackage{lipsum}

%Font
\usepackage[sc]{mathpazo}
\usepackage{courier}

%\oddsidemargin -.5in
%\evensidemargin -.5in
%\bottommargin -0.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0.07in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
		\setlength{\topsep}{0.07in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.0in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0in}}}{\end{list}}

\begin{document}

\renewcommand{\sc}{}
\name{{\Large Chen Lian} \vspace{.08in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
{\it Address:} 
Department of Economics, University of California, Berkeley\\
$~$ \hspace{12mm}
675 Evans Hall, University Dr \\
$~$ \hspace{12mm} 
Berkeley, CA 94720
$~$ \hspace{12mm} \\
  {\it E-mail:} \url{chen_lian@berkeley.edu} \\       
  {\it Website:} \url{https://sites.google.com/view/chenlian/home} \\
  {\it Google scholar:} \url{https://scholar.google.com/citations?user=z3yCoXYAAAAJ&hl=en&oi=sra} 


\section{\sc Academic Positions}

\begin{list1}

\item[] 
\textbf{University of California, Berkeley.} Assistant Professor of Economics (2020--).\\
 Research interests: Macroeconomics, Monetary Economics, Behavioral Economics, Finance.
\vspace{0.2cm}
\item[]
\textbf{National Bureau of Economic Research.} Faculty Research Fellow (2021--). \\
 Programs: Monetary Economics, Economic Fluctuations and Growth.
\end{list1}
\section{\sc Education} 

\begin{list1}
\item[]
\textbf{Massachusetts Institute of Technology}, Cambridge, MA. \\
Ph.D. in Economics, 2020.
\vspace{0.2cm}
\item[]
\textbf{Massachusetts Institute of Technology}, Cambridge, MA.\\
B.S. in Economics, 2015; B.S. in Mathematics, 2015. 
\end{list1}

\section{\sc Working Papers} 
 \begin{list1}
\item[] \textbf{Why do Workers Dislike Inflation? Wage Erosion and Conflict Costs,} with Joao Guerreiro, Jonathon Hazell and Christina Patterson.
\vspace{0.2cm}
\item[] \textbf{Deficits and Inflation: HANK meets FTPL,} with George-Marios Angeletos and Christian Wolf.  
\vspace{0.2cm} 
\item[] \textbf{Beliefs about the Economy are Excessively Sensitive to Household-level Shocks: Evidence from Linked Survey and Administrative Data,} with Dmitry Taubinsky, Luigi Butera and Matteo Saccarola. Under revision for the \emph{Quarterly Journal of Economics}.
\end{list1}

\section{Publications}

\begin{list1}

\item[] \textbf{The Economics of Financial Stress,} with Dmitriy Sergeyev and Yuriy Gorodnichenko. Accepted at \emph{Review of Economic Studies}. 
\vspace{0.2cm}

\item[] \textbf{Can Deficits Finance Themselves?} with George-Marios Angeletos and Christian Wolf. \emph{Econometrica}. September 2024. 
\vspace{0.2cm}

\item[] \textbf{Bankruptcy Resolution and Credit Cycles}, with Martin Kornejew, Yueran Ma, Pablo Ottonello and Diego Perez. \emph{NBER 39th Annual Conference on Macroeconomics}, 2024.
\vspace{0.2cm}

\item[] \textbf{Mistakes in Future Consumption, High MPCs Now.} \emph{American Economic Review: Insights}. December 2023.  
\vspace{0.2cm}

\item[] \textbf{Determinancy without the Taylor Principle,} with George-Marios Angeletos. \emph{Journal of Political Economy}. August 2023.

\vspace{0.2cm}

\item[] \textbf{Dampening General Equilibrium: Incomplete Information and Bounded Rationality,} with George-Marios Angeletos. \emph{Handbook of Economic Expectations}. January 2023.

\vspace{0.2cm}

\item[] \textbf{Confidence and the Propagation of Demand Shocks,} with George-Marios Angeletos. \emph{Review of Economic Studies}. May 2022.
\vspace{0.2cm}

\item[] \textbf{A Theory of Narrow Thinking.}  \emph{Review of Economic Studies}. October 2021 (Feature Article).
\vspace{0.2cm}


\item[] \textbf{Anatomy of Corporate Borrowing Constraints,} with Yueran Ma. \emph{Quarterly Journal of Economics,} February 2021.
\vspace{0.2cm}
\item[] \textbf{Low Interest Rates and Risk Taking: Evidence from Individual Investment Decisions,} with Yueran Ma and Carmen Wang. \emph{Review of Financial Studies}, June 2019 (Lead article).
\vspace{0.2cm}

\item[] \textbf{Forward Guidance without Common Knowledge,} with George-Marios Angeletos. \emph{American Economic Review}, September 2018.
\vspace{0.2cm}

\item[]
\textbf{Incomplete Information in Macroeconomics: Accommodating Frictions in Coordination,} with George-Marios Angeletos. \emph{Handbook of Macroeconomics, Volume 2}, October 2016.

\end{list1}




% \section{\sc Permanent Working Papers} 
% \begin{list1}
% \item[] \textbf{Consumption with Imperfect Perception of Wealth,} December 2019, subsumed into "Mistakes in Future Consumption, High MPCs Now."


% \item[] \textbf{Dampening General Equilibrium,} with George-Marios Angeletos, May 2017, subsumed into "Dampening General Equilibrium: Incomplete Information and Bounded Rationality."
% \end{list1}

\section{\sc Date}

\begin{list1}
\item[] 06/13/2025
\end{list1}

\end{resume}

\end{document}